---
subtitle:  (A Subtitle Would Go Here if This Were a Class)
author: Steven V. Miller
date: 
fontsize: 10pt
logo: noaalogo.jpg
output:
  beamer_presentation:
    theme: "Singapore"
    template: template.tex
    #colortheme: "dolphin"
    fonttheme: "structurebold"
    
in_header: header.tex
#includes:
#in_header: ~/Dropbox/teaching/clemson-beamer-header-simple.txt
#after_body: ~/Dropbox/teaching/table-of-contents.txt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

